Hypercoercions and a Framework for \\ Equivalence of Cast Calculi

### 2020-01-06 paper.tex
related work

\begin{theorem}[\lazyD{} Hypercoercion Respect \ineffCEKD]
  If $\judgetype{\emptyset}{e}{T}$ and $o : T$
  \[
  \text{\evalEqv{\effCEK{H}}{\ineffCEKD}}
  \]
\end{theorem}
\begin{proof}
  Immediately from that every Lazy D Cast ADT is correct ( 
  Theorem~\ref{thm:surely-lazyD-correct}) and that Lazy D hypercoercion is a 
  Lazy D Cast ADT (Lemma~\ref{thm:hc-surely-lazyD}). 
  %
  Alternatively, from Lemma~\ref{thm:SD-equiv},
  Lemma~\ref{thm:hc-surely-lazyD}, Proposition~\ref{thm:LazyD-HC-monoid}, and 
  Proposition~\ref{thm:LazyD-HC-identity-casts}
\end{proof}

>>>>

\begin{theorem}[\lazyD{} Hypercoercion Respect \ineffCEKD]
  If $\judgetype{\emptyset}{e}{T}$ and $o : T$, then
  \[
  \text{\evalEqv{\effCEK{H}}{\ineffCEKD}}
  \]
\end{theorem}
\begin{proof}
  Immediately from that every Lazy D Cast ADT is correct ( 
  Theorem~\ref{thm:surely-lazyD-correct}) and that Lazy D hypercoercion is a 
  Lazy D Cast ADT (Lemma~\ref{thm:hc-surely-lazyD}). 
  %
  Alternatively, from Lemma~\ref{thm:SD-equiv},
  Lemma~\ref{thm:hc-surely-lazyD}, Proposition~\ref{thm:LazyD-HC-monoid}, and 
  Proposition~\ref{thm:LazyD-HC-identity-casts}
\end{proof}

\section{Related Work} \label{sec:related-work}

\newcommand{\lambdaX}[1]{\ensuremath{\lambda\mathtt{#1}}}
\newcommand{\lambdaB}{\lambdaX{B}}
\newcommand{\lambdaS}{\lambdaX{S}}

This section provides a comparison to the work of 
\citet{Siek:2015:BCT:2737924.2737968}. Their blame calculus 
(\lambdaB) is 
similar to our cast calculus (Fig.~\ref{fig:blame-static}). Their \lambdaB\
has base types and primitive operators, while ours has unit, sum, and product.

They define a translation from \lambdaB\ space-efficient coercion calculus 
\lambdaS, which has a space-efficient dynamic semantics, and show a 
bisimulation between \lambdaB\ and \lambdaS. Our work executes the 
source language with a space-efficient abstract machine, thus has no 
\lambdaS-like intermediate language.

A strength of their separation of compilation/translation and execution is that 
they prove the translation is fully abstract and exploit this theorem to prove 
other interesting theorems (Section 5 of \citet{Siek:2015:BCT:2737924.2737968}).

An advantage of our work is that \effCEK{C} and its related theorems are 
parameterized over Lazy D Cast ADT. Their work, on the contrary, is specific to 
their space-efficient coercions.
